Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2024-04-10 doc/manuscript/translocation.qmd
Minor edit to SI CMR methods suggested by Reviewer 3

We estimated survival and recruitment for each site using open population CMR models based on @joseph2018.
For each individual $i=1, ..., M$ on each survey $j=1, ..., n_j$: $o_{i, j} = 1$ if the individual was not detected, and $o_{i, j}=2$ if the individual was detected.
Capture histories of $M$ individuals are modeled, although only $N_s$ individuals were captured.
This parameter expanded data augmentation allows us to capture the possibility that undetected individuals may have recruited into the adult population [@royle2012].
Here, $M$ was chosen to be three times the number of observed individuals ($3N_s$) to be considerably greater than our prior guess of $N_s$.

>>>>

We estimated survival and recruitment for each site using open population CMR models based on @joseph2018.
For each individual in a superpopulation of real and psuedo-individuals, $i=1, ..., M$ on each survey $j=1, ..., n_j$: $o_{i, j} = 1$ if the individual was not detected, and $o_{i, j}=2$ if the individual was detected.
Capture histories of $M$ individuals are modeled, although only $N_s$ individuals were captured.
This parameter expanded data augmentation allows us to capture the possibility that undetected individuals may have recruited into the adult population [@royle2012].
Here, $M$ was chosen to be three times the number of observed individuals ($3N_s$) to be considerably greater than our prior guess of $N_s$.
